The Astropy Project:

### 2017-10-02 main.tex
Update on Overleaf.
s/ngles/angles/

Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays. Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.  In \astropypkg\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.  One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some. As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}). In \astropypkg\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}). As a result, units in fits tables are also well-supported. For most other modules, quantities are at least accepted, and often assumed by default.

@@

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik

@@

    \item[Proper motion and velocity transformations]
    In addition to positional coordinate data, the \texttt{Frame} classes now
    also support velocity data.
    As the default representation for most frames is spherical, most of the
    \texttt{Frame} classes expect proper motion and radial velocity components
    to specify the velocity information.
    The names of the proper motion components all start with \texttt{pm_} and
    adopt the same longitude and latitude names as the positional components.
    Transforming coordinates with velocity data is also supported, but in some
    cases the transformed velocity components have limited accuracy because the
    transformations are done numerically.
    The visualization of the coordinate frame transform graph highlights which
    velocity transformations can be done exactly and which transformations are
    done using a finite-difference scheme.
    The low-level interface for specifying and transforming velocity data (see
    the next point) is currently experimental.
    As such, in v2.0, only the \texttt{Frame} classes (and not the
    \texttt{SkyCoord} class) support handling velocities.

>>>>

Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays. Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.  In \astropypkg\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.  One of the riskiest classes was angles, where both degrees and radians were ``obvious'' default units to some. As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}). In \astropypkg\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}). As a result, units in fits tables are also well-supported. For most other modules, quantities are at least accepted, and often assumed by default.

@@

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik
% TODO: Do we want to put in a PDF of the transform graph?

@@

    \item[Proper motion and velocity transformations]
    In addition to positional coordinate data, the \texttt{Frame} classes now
    also support velocity data.
    As the default representation for most frames is spherical, most of the
    \texttt{Frame} classes expect proper motion and radial velocity components
    to specify the velocity information.
    The names of the proper motion components all start with \texttt{pm} and
    adopt the same longitude and latitude names as the positional components.
    Transforming coordinates with velocity data is also supported, but in some
    cases the transformed velocity components have limited accuracy because the
    transformations are done numerically.
    The visualization of the coordinate frame transform graph highlights which
    velocity transformations can be done exactly and which transformations are
    done using a finite-difference scheme.
    The low-level interface for specifying and transforming velocity data (see
    the next point) is currently experimental.
    As such, in v2.0, only the \texttt{Frame} classes (and not the
    \texttt{SkyCoord} class) support handling velocities.
